---
title: "Phyloseq-preprocessing"
author: "Jiucheng Ding"
date: "`r Sys.Date()`"
output: html_document
---

# Goals of our Pre-Processing File

We will work here in this document to remove any unncessary ASVs or samples, such as: 

1. Mitochondria ASVs. 
2. Chloroplast ASVs.  
3. Deal with the controls:  
    a. ASVs found in the controls.  
    b. Control samples themselves.  
4. Mock ASVs/Mock Community.  
5. Samples that have too few reads for reasonable ecological analysis.


## Load Packages and Functions

```{r load-packages-functions}
# Load Packages
pacman::p_load(tidyverse, phyloseq, install = FALSE)
# Source functions
#source("/local/workdir/jd2263/BIOMI6300_Project2_AmpliconAnalysis/code/functions.R")
#source("/local/workdir/jd2263/BIOMI6300_Project2_AmpliconAnalysis/code/colors_and_shapes.R")
```

## Load the data!

```{r load-data}
# Load in the raw_phyloseq data from DADA2_workflow.Rmd
load("/local/workdir/jd2263/BIOMI6300_Project2_AmpliconAnalysis/data/raw_physeq.RData")
# Take a look at the S4 object!
raw_physeq
# Tell us about you phyloseq!
str(raw_physeq)
typeof(raw_physeq)
#View(raw_physeq@otu_table)
#View(raw_physeq@tax_table)
#View(data.frame(sample_data(raw_physeq)))
```


# Remove unnecessary taxa

We will need to remove the ASVs that are mitochondria, chloroplast or within the mock community. 

```{r rm-ASVs}
# Make a new phyloseq object without the mitochondria, chloroplast or mock community
noMitoChloroCJMock_physeq <- 
  raw_physeq %>%
  # Remove the mitochondria ASVs.  #NOTE THERE WAS A TYPO HERE IN CLASS! 
  subset_taxa(Family != "Mitochondria" | is.na(Family)) %>%
  # Remove the chloroplast ASVs 
  subset_taxa( Order !="Chloroplast" | is.na(Order)) %>%
  # remove the mock community and its ASVs 
  prune_samples(sample_names(.) %!in% c("CJ-V08-P", "MockZymoPos"), .) %>%
  # Now we will remove any ASVs of count 0
  prune_taxa(taxa_sums(.) > 0, .)
# Let's take a look 
noMitoChloroCJMock_physeq
# How many taxa have we removed so far? 
num_ASVs_rm <- ntaxa(raw_physeq) - ntaxa(noMitoChloroCJMock_physeq)
num_ASVs_rm
# Proportion of original data maintained
prop_ASV_rm <- ntaxa(noMitoChloroCJMock_physeq)/ntaxa(raw_physeq)
prop_ASV_rm
```

```{r}
preprocessed_physeq <- noMitoChloroCJMock_physeq
  
```


# Save preprocessed phyloseq!
```{r save-physeq}
save(preprocessed_physeq, file = "/local/workdir/jd2263/BIOMI6300_Project2_AmpliconAnalysis/data/preprocessed_physeq.RData")
```


# Session Information 
```{r}
# Reproducibility
devtools::session_info()
```

